PANCHANGE_variable_creation

### 2020-11-03 PANCHANGE_variable_creation.Rmd
created date variables for 3, 6, 9 months prior to pandemic

@@

>>>>

```{r reorder age_category_collapsed for largest age group as reference category}
dat <- dat %>%
  mutate(age_category_collapsed_reordered = 
           relevel(age_category_collapsed,
                   ref = "26-35", #largest group
                   first = TRUE, #listed first in a list
                   collapse = "+", #string used for combined factor levels
                   xlevels= TRUE #all other levels maintained
                   )
  )
```

@@

Creating variables for subset of participants dependent on when they signed up to GLAD (prepan)
```{r date variables for subset of participants who signed up in 3, 6, 9 months prior to pandemic}
# Date of 3 months prior to the 1st of March
date_3months_prior_march_1st <- as.POSIXct("2019-12-01")

# Date of 6 months prior to the 1st of March
date_6months_prior_march_1st <- as.POSIXct("2019-09-01")

# Date of 9 months prior to the 1st of March
date_9months_prior_march_1st <- as.POSIXct("2019-06-01")
```
